---
title: "Practice 02: Modeling Workflow"
format:
  html:
    toc: true
    toc-depth: 3
    embed-resources: true
---

# Setup

Open this task folder, or its copy under `practice/work/`, as the project for your agent tool. For security, only open the folder you are actively working in.

Use the starter prompt from `practice/prompts/02_modeling-workflow/`. Paste the prompt into the agent rather than placing it in this folder.

```{r}
#| eval: false

data_path <- file.path("data", "maternal_health_data.csv")
maternal <- read.csv(data_path)
```

# Step 1: Inspect Data

Use the agent to help inspect:

- row count
- column count
- variable names
- variable types
- missingness
- suspicious values

```{r}
#| eval: false

dim(maternal)
names(maternal)
str(maternal)
```

# Step 2: Define Outcome

Create `comorbidity_count` from the binary comorbidity indicators.

```{r}
#| eval: false

comorbidity_vars <- c(
  "obesity",
  "multiple_gestation",
  "diabetes",
  "heart_disease",
  "placenta_previa",
  "hypertension",
  "gest_hypertension",
  "preeclampsia"
)

# TODO: check coding of these variables before summing
# TODO: create comorbidity_count
```

# Step 3: Model Planning

Before fitting a model, ask the agent to help inspect the outcome distribution and compare plausible count models.

Questions to answer:

- Is the outcome a count?
- How many zeros are present?
- Is the variance larger than the mean?
- What model assumptions are plausible?
- What diagnostics should be checked?

# Step 4: Interpretation

Keep interpretation tied to the fitted model output.

Use bullets for:

- model choice
- diagnostic checks
- main associations
- limitations

Do not make causal claims.
