---
title: "Find The Analysis Error"
subtitle: "Can an agent catch a serious statistical mistake?"
format:
  html:
    embed-resources: true
    toc: true
---

# Goal

Practice asking an AI tool to audit an analysis for conceptual and statistical errors.

# Dataset

Use:

```text
data/simulated/neighborhood_health_survey_analysis.csv
```

# Flawed Analysis

The analysis below contains a serious problem. Ask an AI tool to review it, then decide whether the tool found the issue.

```{r}
#| eval: false
analysis_df <- read.csv("data/simulated/neighborhood_health_survey_analysis.csv")

fit <- glm(
  adult_high_bp_range ~ systolic_mean + diastolic_mean + age_years + gender + race_ethnicity,
  data = analysis_df,
  family = binomial()
)

summary(fit)
```

# Hint For Instructor

The outcome `adult_high_bp_range` is defined using blood pressure measurements, so using `systolic_mean` and `diastolic_mean` as predictors creates outcome leakage. The model will look strong for the wrong reason.

# Acceptance Criteria

Your report should include:

- What the AI tool identified.
- Whether it found the leakage problem.
- Any false positives or irrelevant critiques.
- A corrected analysis plan.
- A short reflection on how to ask better audit questions.

# Work Area

```{r}
# Start here.
```
