---
title: "Practice Task 1: Clean And Visualize"
format:
  html:
    embed-resources: true
    toc: true
---

> If you use a different analysis method, language, or tool, you will need to adapt this to your set up.

# Goal

Use an AI tool to help clean, summarize, and visualize the county wellness dataset. Check the AI output yourself before trusting it.

# Files

- Dataset: `data/county_wellness_indicators_long.csv`
- Codebook: `data/codebook.md`

# Setup

```{r}
# Add package-loading code here if needed.
```

# Inspect The Data

Use the starter prompt from `practice/prompts/01_clean-and-visualize/` to ask your AI tool to inspect the dataset and codebook before writing the full analysis. Paste the prompt into the agent rather than placing it in this folder.

```{r}
county_wellness <- read.csv("data/county_wellness_indicators_long.csv")

dim(county_wellness)
names(county_wellness)
head(county_wellness)
```

# Clean Or Check The Data

Document any cleaning or checking steps here.

```{r}
# Add cleaning/checking code here.
```

# Summarize The Data

Create a short summary by `measure`, `state_name`, or another relevant grouping variable.

```{r}
# Add summary code here.
```

# Visualize The Data

Create one visualization comparing estimates across measures, states, or counties.

```{r}
# Add visualization code here.
```

# Checks And Reflection

Answer briefly:

- What did the AI tool help with?
- What did you check manually?
- Did the AI tool invent a variable, category, or interpretation?
- What did you revise after checking the output?
