---
title: "Practice Task 1: Clean And Visualize"
format:
  html:
    embed-resources: true
    toc: true
---

> If you use a different analysis method, language, or tool, you will need to set up a workable file for that method. For example, you might use an R script, Python notebook, or Word document instead of this Quarto notebook. Make sure your file can load the data from the course repository and that your final output includes code, results, and your checks.

# Goal

Use an AI tool to help clean, summarize, and visualize the simulated county wellness dataset. Check the AI output yourself before trusting it.

# Files

- Dataset: `data/simulated/county_wellness_indicators_long.csv`
- Codebook: `data/codebooks/simulated_county_wellness_indicators_long.md`
- Prompt: `practice/tasks/01_clean-and-visualize/starter-prompt.txt`

# Setup

```{r}
# Add package-loading code here if needed.
```

# Inspect The Data

Use the prompt file to ask your AI tool to inspect the dataset and codebook before writing the full analysis.

```{r}
county_wellness <- read.csv("data/simulated/county_wellness_indicators_long.csv")

dim(county_wellness)
names(county_wellness)
head(county_wellness)
```

# Clean Or Check The Data

Document any cleaning or checking steps here.

```{r}
# Add cleaning/checking code here.
```

# Summarize The Data

Create a short summary by `measure`, `state_name`, or another relevant grouping variable.

```{r}
# Add summary code here.
```

# Visualize The Data

Create one visualization comparing estimates across measures, states, or counties.

```{r}
# Add visualization code here.
```

# Checks And Reflection

Answer briefly:

- What did the AI tool help with?
- What did you check manually?
- Did the AI tool invent a variable, category, or interpretation?
- What did you revise after checking the output?
